\documentclass[10pt,a4paper]{resume}
\usepackage[left=0.2in,top=0in,right=0.2in,bottom=0.1in]{geometry}
\documentclass{article}
\documentclass{article}
\usepackage{xcolor}
\usepackage{tikz}

% Define the colors
\definecolor{color1}{HTML}{5367FF}
\definecolor{color2}{HTML}{00F3BB}

% \usepackage{helvet}
% \usepackage{hyperref}
\renewcommand{\familydefault}{\sfdefault}
% \usepackage[T1]{fontenc}
\documentclass{article}
\usepackage{tabularx}
\usepackage{hyperref}

% Define custom column types
\newcolumntype{L}{>{\raggedright\arraybackslash}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash}X}

% Define your personal information
\newcommand{\name}{Sarah Khan}
\newcommand{\phone}{+91 8657320043}
\newcommand{\behance}{https://www.behance.net/5arahkhan}
\newcommand{\Github}{https://github.com/Sarahkhan20}
\newcommand{\LinkeIn}{https://www.linkedin.com/in/sarah-khan-13283222a/}
\newcommand{\emaila}{\href{mailto:sarahejaz77@gmail.com}}
\begin{document}
\begin{tabularx}{\textwidth}{@{} L R @{}}
    \Huge \textbf{Sarah Khan} & \multicolumn{1}{c}{\hspace{0cm}} 
 \href{\LinkeIn}{LinkedIN.com/Sarah}  
    \\ Phone: \phone & \href{\Github}{GitHub.com/Sarah} \\ 
    Email: \href{ ContactMe@gmail.com}{\emaila}
 &  \href{\behance}{Behance.com/Sarah}\\
  \end{tabularx}
\end{center}
\begin{tikzpicture}
  \shade[left color=color1, right color=color2] (0,0) rectangle (\textwidth,-1);
  \node[anchor=west, text=white] at (0,-0.5) {\begin{rSection}{Education}
    \end{rSection}};
\end{tikzpicture} \vspace{0.5}
{ University Of Mumbai - Thadomal Shahani Engineering College} \hfill {\it Expected 2025} \\
{\textcolor{Gray}{\it Bachelor of Engineering in Information Technology}} \hfill {\it Mumbai, India}
\begin{itemize}
    \itemsep -1pt
    \item {\underline{Letter Of Appreciation} } for active participation in Developer's Club and CSI Committee, fostering a collaborative and innovative environment.
    \item Participated in {\underline{4+ Hackathons}. }
    \item \underline{Relevant Coursework:} Internet Programming, Data Structures and Algorithm, Database Mngmt., Computer Network, JAVA
\end{itemize}
\end{rSection}
\begin{tikzpicture}
  \shade[left color=color1, right color=color2] (0,0) rectangle (\textwidth,-1);
  \node[anchor=west, text=white] at (0,-0.5) {\begin{rSection}{Skills}
    \end{rSection}};
\end{tikzpicture}
\vspace{0.2}
\begin{tabular}{@{} >{}l @{\hspace{15ex}} l }
{\bf Web:} Reactjs, Next.js, HTML, CSS, JS &{\bf UX:} Research, Wireframing/Prototyping, UI design \\
{\bf Languages:} JavaScript, Java &
{\bf App:} React Native \\
{\bf Tools:} GitHub, Figma, Canva &


\end{tabular}
\end{rSection}
\begin{tikzpicture}
  \shade[left color=color1, right color=color2] (0,0) rectangle (\textwidth,-1);
  \node[anchor=west, text=white] at (0,-0.5) {\begin{rSection}{Experience}
    \end{rSection}};
\end{tikzpicture}
\textbf{The Hobby Tribe} (FrontEnd Developer Intern)
\hfill \textit{Current} 
\begin{itemize}
    \item Created the frontend of the \underline{Teacher management portal} for the Hobby Tribe Team\item  Added \underline{micro-animations}  for the coins and games
\end{itemize}
\end{rSection}

\begin{tikzpicture}
  \shade[left color=color1, right color=color2] (0,0) rectangle (\textwidth,-1);
  \node[anchor=west, text=white] at (0,-0.5) {\begin{rSection}{Projects}
    \end{rSection}};
\end{tikzpicture}
\vspace{0.5}
\textbf{SAATHI} \href{https://www.figma.com/proto/O9QR7OrDTwCQ8Ul6pA02aK/Untitled?node-id=26-15613&starting-point-node-id=26%3A15613&mode=design&t=LV2scfPgpP6qggVR-1}{ & Prototype} \textbar
\href{https://www.figma.com/file/O9QR7OrDTwCQ8Ul6pA02aK/Untitled?type=design&node-id=0%3A1&mode=design&t=lfWNDoS6ngK2ccnn-1}{& Figma Link &}\textbar
\href{https://github.com/Sarahkhan20/Saathi}{ & GitHub & }\textbar
\href{https://sarahkhan.hashnode.dev/saathi-appwrite-hashnode-hackathon}{ & Blog}   

\textcolor{Gray}{\it  Languages: React.js, Appwrite \textbar & Tools: Figma }
\begin{itemize}
    \item Developed \textmd{Saathi}, a platform connecting people in search of \underline{flats and flatmates} leveraging \underline{Appwrite BaAS} Services.
    \item Pioneered a \underline{Tinder-like quiz} to match users based on their preferences, streamlining giving  90\% accurate matches to find perfect flatmate.
\end{itemize}

% \textbf{TURTLEMINT} Chhalaang Hack (HTML, CSS, JS) \href{https://github.com/Sarahkhan20/Chhalaang}{WebApp}

% \textcolor{Gray}{\it Languages: JS }
% \begin{itemize}
% \item Spearheaded a team of 4 and played a pivotal role in \textbf{front-end development} alongside another teammate.
% \item Successfully created a \textbf{car insurance company website comparison portal} using web scraping with \textbf{Beautiful Soup}, facilitating efficient insurance options evaluation for users.
% \end{itemize}
\textbf{PhishNet} (FrontEnd, UX) 
{\textcolor{blue}{\href{https://github.com/Altafalam3/PhishNet}{GitHub}}}


\textcolor{Gray}{\it libraries:React-router, axios,recharts, react-icons, context API}
\begin{itemize}
    \item Engineered \underline{PhishNet, a web security solution} to identify and detect phishing /malicious website.
    \item Solely led \underline{UX design and development} for PhishNet in a \underline{24-hour sprint}, prioritizing dynamic interfaces and user-friendly design. \underline{Integrated payment options, crafted dashboard visuals}, and managed \underline{form requests} seamlessly.
\end{itemize}
\textbf{Swaniti} (Web)   
\href{https://github.com/Sarahkhan20/Swaniti-PROJECT}{ & GitHub }   

\textcolor{Gray}{\it  Languages:HTML5, CSS3, JS}
\begin{itemize}
    \item Swaniti, a portal for \underline{Rural women to learn courses  and find jobs.} Developed \underline{to-do-list, chatbot and pages.}
\end{itemize}

\end{rSection}
\begin{tikzpicture}
  \shade[left color=color1, right color=color2] (0,0) rectangle (\textwidth,-1);
  \node[anchor=west, text=white] at (0,-0.5) {\begin{rSection}{Extra Curricular}
    \end{rSection}};
\end{tikzpicture}
\vspace{0.5}
\textbf{Web Developer} \href{https://github.com/TSEC-MAD-Club}{GitHub} (Next.js)\hfill \textit{Current} \\
\textit{Developer's Club - TSEC} \hfill \textit{Mumbai, India}
\begin{itemize}
\item Mentored \underline{50+ students} in web development
\item Building \underline{panel for teachers, principal and college }committees using \underline{NextJS. }
\end{itemize}
\textbf{Design Team}
\href{https://www.instagram.com/csi_tsec/}{Designs} \hfill \textit{2022 - 2023} \\
\textit{Computer Society Of India - TSEC} \hfill \textit{Mumbai, India}
\begin{itemize}
    \item Organized \underline{48 hours TSEC's Hackathon - RUBIX} with \underline{200+} participants,
handled the \underline{social media, designs, posters.}
\end{itemize}


\end{rSection}
\end{document}
